Comprehensive Quality-Aware Automated Semantic Web Service Composition

### 2017-01-25 paper.tex
up

\section{Related Work} \label{relatedWork}
\textbf{Semantic web service matchmaking}. Substantial work \cite{bansal2016generalized,mier2015integrated,da2016particle,da2015graphevol,yu2013adaptive} on web service composition focused primarily on non-functional requirements consistently neglecting functional requirements. However few researchers addressed both functional and nonfunctional requirements at the same time in web service composition. To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing} reported some recent attempts on service composition that considers both nonfunctional (QoS) and functional (semantic) aspects. Semantic matchmaking utilises Description Logic($DL$) \cite{baader2003description} to search for services that ensure semantic matching utilising an ontology of the corresponding domain.

@@

\textbf{QoS-aware EC approaches}. Evolution Computing techniques are widely used to solve optimisation problems, where the search space is big, so that near-optimised solutions can be found in reasonable time. Genetic Programming (GP) \cite{da2016particle,da2015graphevol} is a typical EC technique applied to automated web service composition. GP-based approaches utilise tree representations, on which service and constructs are represented as terminal nodes and functional nodes respectively. The crossover and mutation operations reproduce various individuals while ensuring the correctness of structure. In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by using a fitness function, which is also liable for the correctness in functionality through penalising infeasible solutions.

@@

The semantic matchmaking is achieved by utilising OWL2 and OWL-S or other semantic markup languages for web services. In this paper, we use MECE (Mediation Contract Extension) \cite{bleul2008self} and OWL-DL. MECE is considered to be an alternative semantic annotation for WSDL. MECE defines the service-related inputs and outputs with parameter-related concepts. OWL-DL is a sublanguage of OWL extended from RDF. It specifies semantic information of concepts involved in MECE. 
\vspace{-0.5cm}
\subsection{Comprehensive Quality Model and Aggregation Matrix}\label{qualityModel}
In this paper, we propose a comprehensive quality model to evaluate the overall quality of semantic web service composition. This model overcome the disadvantages of current prevailing QoS-aware optimisation \cite{bansal2016generalized,mier2015integrated,da2016particle,da2015graphevol,yu2013adaptive} that ignores quality of semantic matchmaking.

@@

The Table \ref{meanFitness} shows the mean fitness values accomplished by two approaches and Table \ref{meanTime} shows the mean execution time required by them. We employ statistical analysis to test the significant differences in mean fitness value and execution time.  The results show that the PSO-based approach performs better in four of five tasks.

@@

We study the mean fitness value with the optimum for both PSO-based and GP-based approach over 30 independent runs. Fig. \ref{psovsgp} is an example of convergence rate performance in WSC09 03, which shows the behaviour of PSO-based approach manifests the characteristics of fast convergence and reaches a better-optimised solution, while the performance of GP is barely satisfactory.

\begin{figure}[h]
\centering
\fbox{\includegraphics[scale=.29]{psovsgp.pdf}}
 \caption{An example of comparing convergency rate from PSO and GP approaches for task 3}
 \label{psovsgp}
\end{figure}

>>>>

\section{Related Work} \label{relatedWork}
\textbf{Semantic web service matchmaking}. Substantial work \cite{bansal2016generalized,mier2015integrated,da2016particle,da2015graphevol,yu2013adaptive} on web service composition focused primarily on non-functional requirements consistently neglecting functional requirements. However few researchers addressed both functional and nonfunctional requirements at the same time in web service composition. To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} reported some recent attempts on service composition that considers both nonfunctional (QoS) and functional (semantic) aspects. Semantic matchmaking utilises Description Logic($DL$) \cite{baader2003description} to search for services that ensure semantic matching utilising an ontology of the corresponding domain.

@@

\textbf{QoS-aware EC approaches}. Evolution Computing techniques are widely used to solve optimisation problems, where the search space is big, so that near-optimised solutions can be found in reasonable time. Genetic Programming (GP) \cite{da2016particle,da2015graphevol} is a typical EC technique applied to automated web service composition. GP-based approaches utilise tree representations, on which service and constructs are represented as terminal nodes and functional nodes respectively. The crossover and mutation operations reproduce various individuals while ensuring the correctness of structure. In \cite{yu2013adaptive}, the author optimises the overall quality of service composition by using a fitness function, which is also liable for the correctness in functionality through penalising infeasible solutions. Also, this paper increase the mutation rate while encountering low diversity in the population and adopt a higher crossover probability while trapped in local optimisation.

A hyper approach employs both a greedy search algorithm and genetic programming is introduced in \cite{ma2015hybrid} to generate locally optimised solution with functionality correctness. In particularly, the greedy search is used to the directed acrylic graph as composite solutions, which is further transferred to tree structure using unfolding techniques as the first generation in GP. In each individual,  terminal nodes are considered as task inputs,  root node as outputs, and inner nodes as atomic web services. During the reproduction process,  a randomly selected node in one individual is replaced with a new subtree generated by a greedy search to perform mutation while same atomic inner nodes in two random chosen individuals are swapped to perform crossover.

@@

The semantic matchmaking is achieved by utilising OWL2 and OWL-S or other semantic markup languages for web services. In this paper, we use MECE (Mediation Contract Extension) \cite{bleul2008self} and OWL-DL. MECE is considered to be an alternative semantic annotation for WSDL. MECE defines the service-related inputs and outputs with parameter-related concepts. OWL-DL is a sublanguage of OWL extended from RDF. It specifies semantic information of concepts involved in MECE.

\subsection{Ontology-based Index Cached Optimisation}
In PSO, particles represent weighted graphs with edges and vertices associated with quality of semantic matchmaking and QoS respectively, the bottlenecks of generating weighted graph lie in building edges and nodes, which are related to the cost of semantic quality calculation and the size of service repository respectively. To effectively construct weighted graphs, we pre-calculate semantic matchmaking quality and mark the input-parameter concepts with a set of services. The key idea of the index is to create a mapping from the output-related concepts to matched input-related services while considering different levels of match types. Furthermore, this index size could also be reduced by only considering parameter-related concepts in the shrunken service repository, which contains  those task-relevant web services. This optimised cache also contributes to less and constant time for weighted graph building for the whole evolutionary process.

\subsection{Comprehensive Quality Model and Aggregation Matrix}\label{qualityModel}
In this paper, we propose a comprehensive quality model to evaluate the overall quality of semantic web service composition. This model overcome the disadvantages of current prevailing QoS-aware optimisation \cite{bansal2016generalized,mier2015integrated,da2016particle,da2015graphevol,yu2013adaptive} that ignores quality of semantic matchmaking.

@@

The Table \ref{meanFitness} shows the mean fitness values accomplished by two methods and Table \ref{meanTime} shows the average execution time required by them. We employ statistical analysis to test the significant differences in mean fitness value and execution time.  The results show that the PSO-based approach performs better in four of five tasks. However, there is also a trade-off between optimised solution and execution time. We can see the PSO-based approach takes longer execution time, it due to that the every individual in each generation must be decoded from generated optimised queue, and this process is very time-consuming. However,  the initialisation first population in GP-based approach is costly in time as transformation process from a DAG, but following new individuals are generated through mutation and crossover, which are considered be much less time consumed comparing decoding process.

@@

\begin{figure}[h]
\centering
\fbox{\includegraphics[scale=.25]{psovsgp.pdf}}
 \caption{An example of comparing convergency rate from PSO and GP approaches for task 3}
 \label{psovsgp}
\end{figure}

We also study the average fitness value with the optimum through the evolutionary process for both PSO-based and GP-based approach over 30 independent runs. Fig. \ref{psovsgp} is an example of convergence rate from Task 3, where the behaviour of PSO-based approach presents a very clear evidence of fast convergence and reaches a better-optimised solution, while the performance of GP is barely satisfactory, as this method improves its fitness value gradually.
